Inefficient Concessions and Mediation

### 2020-03-18 notes.tex
add notes on utility differences between e=0 and e=1 cases

>>>>

\vskip.2in
How does utility compare under $e=1$ and $e=0$? Compare the two, $U_{g_1} \lessgtr U_{g_0}$:
				\[
				  \frac{p}{1-\de_h}T(1+g) + \frac{1-p}{1-\de_h}(W - D(1+g)) - g_h \lessgtr \frac{1}{1-\de_h}\left[pT + (1-p)(W-D) \right] - g_0
				\]
				\[
				  pT(1+g_1) + \left(1-p\right)(W - D(1+g_1)) - \left(1-\de_h\right)g_1 \lessgtr pT + (1-p)(W-D) - \left(1-\de_h\right)g_0
				\]
				\[
				  pTg_1 + \left(1-p\right)(W - D -Dg_1) - \left(1-\de_h\right)g_1 \lessgtr (1-p)(W-D) - \left(1-\de_h\right)g_0
				\]
				\[
				  pTg_1 - \left(1-p\right)Dg_1 - \left(1-\de_h\right)g_1 \lessgtr - \left(1-\de_h\right)g_0
				\]
				\[
				  pTg_1 - \left(1-p\right)Dg_1  \lessgtr \left(1-\de_h\right)g_1 - \left(1-\de_h\right)g_0
				\]
				\begin{equation}
				  pT - \left(1-p\right)D  \lessgtr \frac{\left(1-\de_h\right)\left(g_1 - g_0 \right)}{g_1}
					\label{eq:util}
				\end{equation}

We know (from above) that the minimum gift when $e=1$ is larger than the minimum gift when $e=0$ when
\[
  (1-\de)pT > (1-p)D
\]

\vskip.2in
Let's case this out.
\begin{enumerate}
	\item Assume $g_0 = g_1$; then $(1-\de)pT = (1-p)D$. The right hand side of \ref{eq:util} is 0 and the left hand side is
		\[
			pT - (1-\de)pT = pT - pT + \de pT = \de pT 
		\]
		And utility under $e=1$ is higher.
	\item When $g_0 > g_1$; then $(1-\de)pT < (1-p)D$. The right hand side of \ref{eq:util} is negative and the left hand side is larger (more positive) than in case 1, so utility under $e=1$ is also higher in this case.
	\item When $g_1 > g_0$; then $(1-\de)pT > (1-p)D$. The right hand side of \ref{eq:util} becomes positive and the left hand side becomes smaller (less positive, and possibly negative) than in case 1, so utility under $e=1$ is higher when $g_1$ is only a little larger than $g_0$, but eventually as $g_1$ gets much larger than $g_0$, utility under $e=0$ becomes larger than utility under $e=1$.
\end{enumerate}
